Road User video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-07-29 README.qmd
Update with cjs codes
Update readme
update readme
md version
Add bib

@@

```r
remotes::install_github("ITSLeeds/opsnap")
```

>>>>

# Note

This package is in development and not yet on CRAN.
If you would like to use it, please install it from GitHub as shown below, and cite it as follows:

Farrell, G., Lovelace, R., & O'Hern, S. (2024). Road User Video Evidence of Road Traffic Offences: Preliminary Analysis of Operation Snap Data and Suggestions for a Research Agenda. https://doi.org/10.31235/osf.io/cgjmr

```
@misc{farrellRoadUserVideo2024,
  title = {Road {{User Video Evidence}} of {{Road Traffic Offences}}: {{Preliminary Analysis}} of {{Operation Snap Data}} and {{Suggestions}} for a {{Research Agenda}}},
  shorttitle = {{{ROAD USER VIDEO EVIDENCE OF ROAD TRAFFIC OFFENCES}}},
  author = {Farrell, Graham and Lovelace, Robin and O'Hern, Steve},
  year = {2024},
  month = jul,
  publisher = {OSF},
  doi = {10.31235/osf.io/cgjmr},
  urldate = {2024-07-29},
  archiveprefix = {OSF},
  langid = {american},
  keywords = {antisocial driving,dangerous driving,near misses,Operation Snap,OpSnap,roas safety,Video evidence}
}

Read the full paper [here](https://osf.io/cgjmr/download/).

@@

```{r}
#| eval: false
remotes::install_github("ITSLeeds/opsnap", force = TRUE, dependencies = TRUE)
```
